Fast Algorithms for Intersection of Non-matching Grids Using \plucker coordinates.

### 2016-09-30 paper_intersections.tex

\section{Benchmarks}
In this section we present numerical results on several benchmark problems. At first we shall compare 
the effectivity of our fundamental algorithms for intersections with other approaches.

@@

\section{Conclusions}
TODO:
- line intersection tracking for accelerate 2D-2D intersections
- better handling of special cases in paarticular in relation to prolongations
- better calculation reuse (pass with prolongations)
- optimisation of element intersection - skip unnecessary calculations
\section{Acknowledgement}
The paper was supported in part by the Project OP
VaVpI Centre for Nanomaterials, Advanced Technologies  and Innovations
CZ.1.05/2.1.00/01.0005.

>>>>

\section{Benchmarks}
\label{sec:benchmarks}
In this section we present numerical results on several benchmark problems. At first we shall compare 
the effectivity of our fundamental algorithms for intersections with other approaches.

@@

\section{Conclusions}
\label{sec:conclusins}

TODO:
- line intersection tracking for accelerate 2D-2D intersections
- better handling of special cases in paarticular in relation to prolongations
- better calculation reuse (pass with prolongations)
- optimisation of element intersection - skip unnecessary calculations
%\section{Acknowledgement}
%The paper was supported in part by the Project OP
%VaVpI Centre for Nanomaterials, Advanced Technologies  and Innovations
%CZ.1.05/2.1.00/01.0005.
